Sentiment Analysis of Twitter in Relation to Fossil Fuel Stock Prices

### 2023-04-28 manuscript/manuscript.tex
final edits

Although this study found that both weighted and unweighted sentiment scores may not have been effective in predicting stock price movement and volatility of CVX, it established a novel methodology for analyzing Twitter sentiment data and determining whether it is informative in predicting stock prices. This methodology can be applied to other industries and sectors to gain a better understanding of the role that sentiment plays in stock price movements. The methodology can be useful for multiple groups, such as Public Relations departments in companies like Chevron, who can use this to assess the effectiveness of their publicity campaigns on the company's valuation, leading to higher profits and public influence. Alternatively, environmental groups can use this methodology to measure the effectiveness of their activism campaigns in influencing the trading power of Chevron Stock ownership. This methodology provides a way for various groups to adjust their strategies to influence public sentiment and in turn stock value.

Overall, this study provides valuable insights into the use of Twitter sentiment analysis as a tool for predicting stock prices, and points towards potential avenues for further research. With further research, determined but analyzing the effect of public sentiment on stock prices of fossil fuel companies can provide valuable insight into how public opinion can be used to augment or reduce the effects of climate change.

>>>>

While this study did not find weighted and unweighted sentiment scores to be effective in predicting stock price movements and volatility of CVX, it introduced a novel approach to analyzing Twitter sentiment data and evaluating its predictive value for stock prices. This methodology can be applied in other industries and sectors to gain a better understanding of the role that sentiment plays in stock price movements. The methodology can be helpful to various groups, such as Public Relations departments in companies like Chevron, who can use this to assess the effectiveness of their publicity campaigns on the company's valuation, leading to higher profits and public influence. Alternatively, environmental groups can use this methodology to measure the effectiveness of their activism campaigns in influencing the trading power of Chevron Stock ownership. This methodology provides a way for various groups to adjust their strategies to influence public sentiment and in turn stock value.

Overall, this study provides valuable insights into the use of Twitter sentiment analysis as a tool for predicting stock prices, and points towards potential avenues for further research.
